\chapter{Conclusion and Future Work}

\section{Conclusion}
Digital entertainment has grown faster than our ability to navigate it. Audiences now face enormous, continuously expanding catalogues of films and games, and the practical effect is not abundance but paralysis: discovery is fragmented across separate, domain-specific services, and the effort of deciding what to watch or play has itself become a source of fatigue. The problem this work set out to solve is precisely this fragmentation---the absence of a single system that understands a person's taste in \emph{both} films and games and turns that understanding into relevant, safe, and socially-aware recommendations.

In this documentation we presented \textbf{Questro}, our answer to that problem, and discussed each part of how it was conceived, designed, and built. We discussed the cross-domain recommendation model---\textbf{CL-EPIDTN}, a dual-tower Transformer trained with a multi-objective contrastive criterion (InfoNCE together with self-supervised and modality-matching losses) and fused with content and collaborative signals through reciprocal rank fusion---that places movies and games in one shared taste space; the retrieval-augmented conversational assistant, which pairs semantic vector search over a memory-mapped FAISS index with a grounded large language model (Google Gemini), letting users discover content through natural language while remaining anchored in real catalogue data; the backend that orchestrates these services securely and statelessly; the dual-token authentication and parental-control mechanisms that keep the platform safe, especially for younger users; and the responsive client through which all of this is delivered.

The results obtained are encouraging given the difficulty of the problem. Our recommendation model was trained on two large public sources of behaviour---one for films and one for games---that share \emph{no} common users, so the model cannot simply memorize who-likes-what across the two domains; it must learn genuine cross-domain structure from content and interaction patterns. Evaluated honestly against the entire catalogue of roughly $138{,}000$ titles, rather than against an artificially small pool of candidates, the model places a user's true next item within its top fifty suggestions for close to one user in five. Because the odds of doing this by chance over a catalogue of that size are on the order of one in ten thousand, the result shows that the model is recovering real cross-domain preference signal rather than echoing popularity.

The conversational assistant performed reliably across a broad battery of evaluation queries spanning coherent profiles, cross-domain requests, title-based lookups, and edge cases. It answered every query without failure, blended both entertainment domains in roughly seven of every ten responses, and surfaced the expected target item in two out of three fact-checked probes, while consistently honouring the parental-control restrictions enforced before any candidate ever reaches the language model. In short, the assistant delivers grounded, personalized, and safe recommendations in natural language.

Measured against other projects, this outcome is best understood in context. The one directly comparable point of reference is \textbf{AutoCDSR} \cite{ju2025autocdsr}, a published cross-domain sequential recommender that we re-implemented and trained through Questro's \emph{exact} data pipeline and evaluated under the identical full-catalogue protocol; against it, CL-EPIDTN is uniformly stronger, raising the top-50 hit rate from $0.151$ to $0.185$ and the top-10 hit rate from $0.063$ to $0.071$. Recognized single-domain recommendation models report higher headline accuracy, but they are designed and evaluated within a \emph{single} domain and against a small set of sampled alternatives---a markedly easier setting than the one Questro addresses \cite{kang2018sasrec, sun2019bert4rec, hidasi2016gru4rec, tang2018caser}. Existing entertainment platforms, likewise, excel in one domain but treat films and games as separate worlds \cite{ref:cross_domain_survey}. Questro's contribution is therefore not to beat single-domain accuracy scores on their own terms, but to solve a strictly harder problem that those projects do not attempt: unifying two distinct entertainment domains, with no shared users, into one coherent, safe, and socially-enriched recommendation experience. Within that harder setting, our system demonstrably works end to end.

\section{Future Work}
Questro is a complete and functional system, but several directions would meaningfully extend its data, intelligence, and reach. The most impactful targets the data the model learns from; the remainder strengthen the conversational pipeline and the wider platform.

\subsection{Enriching the Model with Physical-Media Reviews}
\label{sec:future_physical_reviews}
The single most valuable extension concerns the training data itself. Our current behavioural data is drawn entirely from \emph{digital-first} sources, which overlook the large population of people who buy and review \textbf{physical copies} of games and films. A natural next step is to gather ratings and written reviews of boxed and physical editions from online retail and marketplace storefronts, match them against our existing catalogue, and fold them into the training data as additional signals.

This enrichment is attractive for three reasons. First, it substantially increases the volume and coverage of behavioural data, including older titles and audiences that digital-only sources under-represent, which directly eases the data-sparsity and cold-start pressures every recommender faces \cite{ref:cold_start}. Second, and most importantly, retail shoppers frequently buy \emph{both} films and games from the same storefront, which introduces the genuine cross-domain user overlap that our current movie-and-game sources structurally lack; learning from people who demonstrably consume both media types would let the model ground its cross-domain alignment in real shared behaviour rather than inferring it purely from content \cite{ref:cross_domain_survey}. Third, the review text is itself a rich signal: a sentiment-analysis stage could convert written opinions into the same normalized preference weights the model already consumes, turning qualitative reviews into quantitative training targets \cite{taha2024}.

Realizing this pipeline raises practical challenges that future work must address: respecting the terms of service and legal constraints of each data source, reliably matching physical editions to existing catalogue entries, filtering promotional and spam reviews, and correcting for the differing rating habits of retail versus enthusiast audiences. Handled carefully, this single addition would expand both the size and the cross-domain richness of the training data more than any change to the model itself.

\subsection{Conversational Assistant Enhancements}
The retrieval-augmented assistant offers several clear improvements:
\begin{itemize}
    \item \textbf{Conversational memory.} The assistant currently answers each query independently. Maintaining dialogue state across a session would let it handle follow-up and refinement requests (``something lighter than that'', ``but for two players'') and progressively narrow recommendations through a conversation.
    \item \textbf{Hybrid retrieval.} Semantic search captures meaning but can miss exact titles and rare keywords. Combining it with a classical lexical retriever such as BM25 \cite{robertson2009bm25} would improve recall for precise queries while preserving broad semantic matching.
    \item \textbf{Stronger reranking.} A lightweight cross-encoder that jointly reads the query and each candidate \cite{nogueira2019passage} could sharpen the ordering of retrieved items before personalization, improving the quality of what the language model ultimately sees.
    \item \textbf{Lower latency.} End-to-end response time is dominated by the external language-model call. Streaming the response to the user as it is generated would greatly reduce perceived waiting, and a smaller or self-hosted model would reduce absolute latency under heavy load.
    \item \textbf{Caching and feedback learning.} Caching results for popular queries would cut both latency and cost, while a simple thumbs-up/thumbs-down channel would supply feedback for continuously improving retrieval and ranking quality.
\end{itemize}

\subsection{Recommendation Model Enhancements}
Several extensions would deepen the recommender beyond its current form:
\begin{itemize}
    \item \textbf{Online and incremental learning.} The model is presently trained offline. An incremental-update path would let newly observed interactions refresh the model without a full retrain, keeping recommendations current as the user base grows.
    \item \textbf{Native cross-domain histories.} Once real users accumulate genuine cross-domain interaction histories on the platform, the model can be fine-tuned on that in-house behaviour, complementing the public-data pre-training with patterns observed on Questro itself.
    \item \textbf{Multimodal item understanding.} Incorporating poster images, screenshots, and trailers through pre-trained vision models would enrich item representations with visual semantics, complementing the current text-and-metadata content signal.
    \item \textbf{Online evaluation.} Offline accuracy tells only part of the story. Controlled live experiments measuring real engagement (click-through, dwell time, conversions) would validate offline gains against genuine user satisfaction and guide diversity and serendipity tuning.
\end{itemize}

\subsection{Platform and Infrastructure Enhancements}
Finally, the broader system would benefit from operational and feature investment: containerized, autoscaling deployment with a distributed cache to support large concurrent loads; end-to-end monitoring and tracing to make failures diagnosable in production; further security hardening through cross-property validation, request rate-limiting, and periodic penetration testing; and broader reach through native mobile clients, real-time social notifications, internationalization, and accessibility improvements.

\section{Closing Remarks}
Questro demonstrates that the two largest pillars of interactive entertainment---film and gaming---can be served from a single, coherent, and safety-aware recommendation platform, and that a cross-domain model can be made to work end to end even without shared users between its training sources. The directions outlined above, led by the enrichment of the training data with physical-media reviews, chart a clear path from this working system toward a richer, faster, and more deeply personalized successor.
